---
title: "Weight of Fish"
author: "Jayline Zelaya"
date: "Fall 2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(dplyr)
library(leaps)
fish = read_csv("Fish.csv")
```

# Predicting Fish Weight

Find the best model using 2 variables to predict Perch weight, and compare this to the best overall model.

## Perch

```{r}
perch = filter(fish, Species == 'Perch')
```




```{r}
modelPerch = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = perch)
summary(modelPerch)
```





### Best Two regressor model




```{r}
best2Perch = lm(Weight ~ Height + Width, data=perch )
summary(best2Perch)
```

P value is .00000000000000022


### Best 2 variable equation

Weight = -536 + 74.77*Height + 69.62* Width




## Pike

```{r}
pike = filter(fish, Species == 'Pike')
```



```{r}
modelPike = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = pike)
summary(modelPike)
```


### Best Two regressor model

```{r}
best2Pike = lm(Weight ~ Length1 + Length3, data=pike )
summary(best2Pike)
```

### Best 2 variable equation

Weight = -1675.79 + -105.64 *Length1 + 145.25* Length3



## Roach

```{r}
roach = filter(fish, Species == 'Roach')
```




```{r}
modelRoach = regsubsets(Weight ~ Length1 + Length2 + Length3 + Height + Width, data = roach)
summary(modelRoach)
```




### Best Two regressor model

```{r}
best2Roach = lm(Weight ~ Length3 + Width, data=roach )
summary(best2Roach)
```


### Best 2 variable equation

Weight = -319.118 + 8.278  *Length3 + 72.300 * Width

## Final Summary Statements



